Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations

### 2021-05-06 doc/main_jfm.tex
adding some texts

The preliminary test of the proposed model using integral equation method is the Jeffery orbits of single ellipsoidal particle under a shear flow. A particle is initially placed with its center of mass fixed at the origin and the angle between the major axis and the $y$-axis is denoted as $\chi = 0^\circ$. Based on the theoretical Jeffery orbits with respect to the target angle,

\begin{equation}
\chi(t) = \tan^{-1}\left(\frac{a}{b}\tan \left(\frac{ab \dot\gamma t}{a^2+b^2}\right)\right),
\end{equation}
%
where $a$, $b$ are semi-major and semi-minor axes, $\dot\gamma$ is the shear rate, and the test aspect ratio of the particle is $2$. Figure~\ref{figure1} shows that the proposed integral equation method has a perfect agreement with the theoretical result from Jeffery orbits.

\begin{figure}[H]
\begin{center}
\includegraphics[width=0.5\textwidth]{JefferyOrbit.eps}
\end{center}
  \caption{Comparison of the target angle $\chi(t)$ versus time $t$ between the theoretical Jeffery orbit and the result from the integral equation method. The schematic of the simulation setup is shown in the inset of the figure.
  }
    \label{figure1}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.3\textwidth]{N58_0.eps}
\includegraphics[width=0.3\textwidth]{N58_20000.eps}
\end{center}
  \caption{Vesicle under a shear flow where the shear rate $\dot\gamma=0.005$: 
  (a) Initial configuration of 58-body vesicle; (b) Deformed vesicle.
  }
    \label{figure2}
\end{figure}
%

@@

Figure~\ref{figure5} shows two sets of simulations. Starting from the initial configuration (shown in panel (a)), panels (b)-(d) show the transitions of two vesicles moving under an extensional flow. The flow is stretching along the $y$ direction and squeezing in $x$ direction. Hence two vesicles are first pushed toward each other  then separate. With the same starting state, panels (e)-(h) are the observed phenomena when two vesicles are in a shear flow $x = \dot\gamma y$. An interesting event occurs in the simulation that a rotational behavior with an adhesive effect can be observed and tuned.

>>>>

The preliminary test of the proposed model using integral equation method is the Jeffery orbits of single ellipsoidal particle under a shear flow $\dot x = \dot\gamma y$ where $\dot\gamma$ is the shear rate. A particle is initially placed with its center of mass fixed at the origin and the angle between the major axis and the $y$-axis is denoted as $\chi = 0^\circ$. Based on the theoretical Jeffery orbits with respect to the target angle,

\begin{equation}
\chi(t) = \tan^{-1}\left(\frac{a}{b}\tan \left(\frac{ab \dot\gamma t}{a^2+b^2}\right)\right),
\end{equation}
%
where $a$, $b$ are semi-major and semi-minor axes, and the test aspect ratio of the particle is $2$. Figure~\ref{figure1} shows that the proposed integral equation method has a perfect agreement with the theoretical result from Jeffery orbits.

\begin{figure}[H]
\begin{center}
\includegraphics[width=0.4\textwidth]{JefferyOrbit.eps}
\end{center}
  \caption{Comparison of the target angle $\chi(t)$ versus time $t$ between the theoretical Jeffery orbit with $\dot\gamma=0.1$ and the result from the integral equation method. The schematic of the simulation setup is shown in the inset of the figure.
  }
    \label{figure1}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.3\textwidth]{N58_0.eps}
\includegraphics[width=0.3\textwidth]{N58_20000.eps}
\end{center}
  \caption{Vesicle under a shear flow where the shear rate $\dot\gamma=0.005$: 
  (a) Initial configuration of 58-body vesicle; (b) Deformed vesicle after $20000$ steps. The tank-treading motion occurs after reaching the state shown in panel (b).
  }
    \label{figure2}
\end{figure}
%

@@

Figure~\ref{figure5} shows two sets of simulations. Starting from the initial configuration (shown in panel (a)), panels (b)-(d) show the transitions of two vesicles moving under an extensional flow. The flow is stretching along the $y$ direction and squeezing in $x$ direction. Hence two vesicles are first pushed toward each other  then separate. With the same starting state, panels (e)-(h) are the observed phenomena when two vesicles are in a shear flow $\dot x = \dot\gamma y$. An interesting event occurs in the simulation that a rotational behavior with an adhesive effect can be observed and tuned.
